---
title: "VISIR-DB Report"
author: "VISIR-DB"
output:
  html_document:
    self_contained: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Set Main Features

The analyzed data set, **`r logFileName_ext`**, includes `r nrow(dfActionTime_ext)` actions from `r min(as.POSIXct(dfActionTime_ext$FechaHoraEnvio))` to `r max(as.POSIXct(dfActionTime_ext$FechaHoraEnvio))`.

### Users
There are `r length(unique(dfActionTime_ext$Alumno))` unique users in the data set. Their IDs are...<br />
`r paste(unique(dfActionTime_ext$Alumno), sep="; ")`.

### Work Indicators
There are `r ncol(dfObsItems_xUser_ext) - 1` observation items in **`r oiFileName_ext`**: <br />`r paste(colnames(dfObsItems_xUser_ext[,-1]), sep="; ")`.

``` {r, echo=F, include = T, results="asis"}
emExist <- exists("emFileName_ext") 
cat(ifelse(!emExist,"<!--",""))
```

There are `r ncol(dfEvMilestones_xUser_ext) - 2` assessment milestones in **`r ifelse(emExist,emFileName_ext,"")`**: <br /> `r paste(colnames(dfEvMilestones_xUser_ext[,-c(1,ncol(dfEvMilestones_xUser_ext))]), sep="; ")`.

``` {r, echo=F, include = T, results="asis"}
cat(ifelse(!emExist, "-->", "<!--"))
```

Assessment milestones are not loaded and observation milestones will be used instead.

``` {r, echo=F, include = T, results="asis"}
cat(ifelse(emExist, "-->", ""))
```


## Global Results

### Time

#### Time on Task Distribution

``` {r, echo=F}
plotDistribution(sumxStud_ext$TotalTime, xlabel="Time per User, in h")
```

#### Time on Task vs User per Date -- HeatMap

``` {r, echo=F}
dfACxSD <- expand.grid(Dates=as.character(
      seq(min(as.Date(sumxStudDate_ext$Dates)),
          max(as.Date(sumxStudDate_ext$Dates)),by=1)),
      Alumno = levels(sumxStudDate_ext$Alumno))

dfACxSD <- merge(dfACxSD,sumxStudDate_ext,all=T)
dfACxSD$Alumno <- factor(dfACxSD$Alumno,
                             levels(sumxStudDate_ext$Alumno),
                             ordered=T)
g <- dfACxSD %>%  
  mutate (TimeInDate = round(TimeInDate/60, digits=2)) %>% 
  ggplot(aes(x = Alumno, y = Dates)) + theme_bw() +
  geom_tile(aes(fill=TimeInDate),width=0.9) + 
  labs(x="User", y="Date") +
  theme(axis.title = element_text(size=14),
        axis.text= element_text(size=11),
        legend.position = "top",
        legend.title = element_text(size=14),
        legend.text= element_text(size=11),
        axis.text.x=element_text(angle = 90, vjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))+
  scale_fill_viridis(name="Time, in h",direction=-1,
                     na.value=rgb(1,1,1,0))

if(length(unique(sumxStudDate_ext$Alumno)) > 30) g <- g +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5, size = 9)) 
if(length(unique(sumxStudDate_ext$Alumno)) > 50) g <- g +
  theme(axis.text.x = element_blank())
if(length(unique(sumxStudDate_ext$Dates)) > 30) g <- g +
  theme(axis.text.y = element_blank())
g

```

### Experiments

#### Experimental Timelines

```{r, echo=F}
gra=c("red","green","blue","black")

g <- dfActionCircuit_ext %>% mutate (Time = round(Time/60, digits=2)) %>% 
  ggplot(aes(x = Alumno, y = Time, 
             color = Measure, shape= Measure)) + 
  geom_line(aes(x=Alumno, y=TotalTime, color=NULL, shape=NULL, group=1),
            data=sumxStud_ext, color="grey") + 
  geom_point(size = 4, alpha = 0.5) +
  labs(y="Time, in h", x = "User") +
  scale_color_manual(values = gra) +
  scale_shape_manual(values= c(95,95,95,13)) +
  theme(panel.background = element_rect(fill=NA), 
        panel.border = element_rect(colour="black",fill=NA),
        panel.grid.major.x = element_line(linetype=0),
        panel.grid.major.y = element_line(colour="lightgray",linetype="solid"),
        legend.key=element_blank(),
        legend.position= "top",
        legend.title = element_text(size=14),
        legend.text= element_text(size=11),
        axis.title = element_text(size=14),
        axis.text= element_text(size=11),
        axis.text.x=element_text(angle = 90, vjust = 0.5))+
  guides(color = guide_legend(override.aes = list(size=9)))  

if(nrow(sumxStud_ext)>30) g <- g +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5, size = 9))         

if(nrow(sumxStud_ext)>50) g <- g + theme(axis.text.x = element_blank())

g
```

#### Experiments per User and Date -- Heat map

```{r, echo=F}
dfACxSD <- expand.grid(
  Dates=as.character(
      seq(min(as.Date(sumxStudDate_ext$Dates)),
          max(as.Date(sumxStudDate_ext$Dates)),by=1)),
  Alumno = levels(sumxStudDate_ext$Alumno))
dfACxSD <- merge(dfACxSD,sumxStudDate_ext,all=T)

dfACxSD$Alumno <- factor(dfACxSD$Alumno,
                         levels(sumxStudDate_ext$Alumno),
                         ordered=T)

g <- ggplot(data = dfACxSD, aes(x = Alumno, y = Dates)) + theme_bw() +
  geom_tile(aes(fill=NumCircu), width=0.9) +
  labs(x ="User", y= "Date") +
  theme(axis.title = element_text(size=14),
        axis.text= element_text(size=11),
        legend.position = "top",
        legend.title = element_text(size=14),
        legend.text= element_text(size=11),
        axis.text.x=element_text(angle = 90, vjust = 0.5),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
  scale_fill_viridis(name="Experiments",direction=-1,
                     na.value=rgb(1,1,1,0))

if(length(unique(sumxStudDate_ext$Alumno)) > 30) g <- g +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5, size = 9)) 
if(length(unique(sumxStudDate_ext$Alumno)) > 50) g <- g +
  theme(axis.text.x = element_blank())
if(length(unique(sumxStudDate_ext$Dates)) > 30) g <- g +
  theme(axis.text.y = element_blank())
g
```

### Experiments vs Time 

#### Number of Experiments vs Time

```{r, echo=F}
meanTT <- mean(sumxStud_ext$TotalTime)
meanNC <- mean(sumxStud_ext$NumCircu)
maxTT <- max(sumxStud_ext$TotalTime)
maxNC <- max(sumxStud_ext$NumCircu)

ggplot(sumxStud_ext, aes(x=TotalTime, y=NumCircu))  +  
  geom_point(size = 3, alpha = 0.4) + 
  labs(x = "Time, in h", y = "Number of Experiments") +
  geom_hline(yintercept = meanNC, color="#fbada7")+
  geom_vline(xintercept = meanTT, color="#66d9dc") +
  geom_text(aes(x = (meanTT + maxTT)/2, y= meanNC, label=round(meanNC,digits = 2))) +
  geom_text(aes(x = meanTT, y= (meanNC + maxNC)/2, label=round(meanTT,digits = 2))) + 
  geom_text_repel(aes(label=Alumno)) +
  theme_bw() + 
  theme(axis.title = element_text(size=14),
        axis.text= element_text(size=11),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
```

## Circuit-based Analysis

### Measurement Types
The data set includes `r nrow(dfActionCircuit_ext)` circuits, which can be traced to the following measurement types:

```{r, echo=F}
df <- as.data.frame(table(dfActionCircuit_ext$Measure))
colnames(df) <- c("Measurement", "Count")
kable(df)
```

### Common Circuits

The 10 top common normalized circuits are 

```{r, echo=F}
tab <- table(na.omit(dfActionCircuit_ext$CircuitoNormalizado))
tab <- tab[order(-tab)]
df <- data.frame(Circuit = names(tab), TimesTested = as.integer(tab),
               stringsAsFactors = FALSE)
df <- df[order(df$TimesTested, decreasing=T),][1:10, ]
kable(df)
```


The 10 top common simplified circuits are 

```{r, echo=F}
tab <- table(na.omit(dfActionCircuit_ext$CircuitoSimplificado))
tab <- tab[order(-tab)]
df <- data.frame(Circuit = names(tab), TimesTested = as.integer(tab),
               stringsAsFactors = FALSE)
df <- df[order(df$TimesTested, decreasing=T),][1:10, ]
kable(df)
```


### Common Errors

The 10 top common normalized circuits which are detected as errors, are 

```{r, echo=F}
tab <- table(na.omit(dfActionCircuit_ext$CircuitoNormalizado[
  dfActionCircuit_ext$Measure=="Error"]))
tab <- tab[order(-tab)]
df <- data.frame(Circuit = names(tab), TimesTested = as.integer(tab),
               stringsAsFactors = FALSE)
df <- df[order(df$TimesTested, decreasing=T),][1:10, ]
kable(df)
```


## Work Indicators

### Observation Items

#### Group Performance

```{r, echo=F}
visirtrMilestonesDifficulty(dfObsItems_xUser_ext)
```  

#### Performance per User

```{r, echo=F}
g <- visirtrHeatMapAchievedMilestonePerId(dfObsItems_xUser_ext,labels=NULL) +
  theme(legend.position = "top",
        legend.title=element_text(size=14),
        legend.text=element_text(size=11))

if(length(unique(dfObsItems_xUser_ext$Alumno)) > 30) g <- g +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5, size = 9)) 
if(length(unique(dfObsItems_xUser_ext$Alumno)) > 50) g <- g +
  theme(axis.text.x = element_blank())
g

```

### Assessment Milestones

#### Group Performance

```{r, echo=F}
visirtrMilestonesDifficulty(dfEvMilestones_xUser_ext[, -ncol(dfEvMilestones_xUser_ext)])
```  

#### Performance per User

```{r, echo=F}
g <- visirtrHeatMapAchievedMilestonePerId(
  dfEvMilestones_xUser_ext[, -ncol(dfEvMilestones_xUser_ext)],
  labels=NULL) + theme(legend.position = "top",
                       legend.title=element_text(size=14),
                       legend.text=element_text(size=11))

if(length(unique(dfEvMilestones_xUser_ext$Alumno)) > 30) g <- g +
  theme(axis.text.x=element_text(angle = 90, vjust = 0.5, size = 9)) 
if(length(unique(dfEvMilestones_xUser_ext$Alumno)) > 50) g <- g +
  theme(axis.text.x = element_blank())
g

```


## User-specific Results

The summarized results for the `r nrow(sumxStud_ext)` users are shown in the table below, in alphabetical order.

```{r, echo=F}
df <- merge(sumxStud_ext,dfEvMilestones_xUser_ext)
df <- df[,c(1:2,4,8:11, ncol(df))]
colnames(df) <- c("User", "Time on Task", "Number of Experiments",
                  "Errors", "Current", "Voltage", "Resistance", 
                  "Grade")
kable(df)
```

